\thetitle

### 2020-10-22 sun_phases/spin_qudit_tomo.tex
minor change to appendix

\begin{abstract}
  We consider the task of performing quantum state tomography on a $d$-state spin qudit, using only measurements of spin projection onto different quantization axes.
  We map this quantum tomography problem onto the classical problem of signal recovery on the sphere, thereby proving that full reconstruction of arbitrary mixed states is possible and requires a minimum number of measurement axes, $r_d$, that is bounded by $2d-1\le r_d\le d^2$.
  Our mapping comes with a straightforward prescription for converting existing signal recovery algorithms into spin qudit tomography protocols, and numerical experiments show that $r_d=2d-1$ for $d\le20$.
  [\red{Note: there are also a few other things that I want to look into, including (1) a simplified tomography procedure for pure states, (2) trade-offs between measurement precision and the \# of measurement axes (for a fixed total number of measurements; these will likely be numerical experiments), (3) proofs about the something like the number of measurements necessary to reconstruct an arbitrary state to a given precision, and (4) adaptive tomography protocols.]}
\end{abstract}

>>>>

\begin{abstract}
  We consider the task of performing quantum state tomography on a $d$-state spin qudit, using only measurements of spin projection onto different quantization axes.
  By mapping this quantum tomography problem onto the classical problem of signal recovery on the sphere, we prove that full reconstruction of arbitrary mixed states is possible, and requires a minimum number of measurement axes, $r_d$, that is bounded by $2d-1\le r_d\le d^2$.
  We provide explicit optimized tomography protocols, and show that $r_d=2d-1$ for $d\le20$ with numerical experiments.
  [\red{Note: there are also a few other things that I want to look into, including (1) a simplified tomography procedure for pure states, (2) trade-offs between measurement precision and the \# of measurement axes (for a fixed total number of measurements; these will likely be numerical experiments), (3) proofs about the something like the number of measurements necessary to reconstruct an arbitrary state to a given precision, and (4) adaptive tomography protocols.]}
\end{abstract}
